---
title: "Mine Basin Regressions"
author: "Lukas Vashold"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Description

This Markdown contains preliminary results for RDD regressions of mines and their effects on agricultural productivity. The structure of the document is as follows:

```{r prelims, include=FALSE}
library("dplyr")
library("readr")
library("fixest")
library("pdftools")
sapply(list.files("R", ".R$"), \(f) {source(paste0("R/", f)); TRUE})

df_reg <- readRDS(p("processed/df_reg.RDS"))
```


## Main Models

### Full sample

This specification includes:

* all years from **2001 to 2023**
* all basin systems, regardless of area mined in the mine basin itself
* all up/downstream basins up to **10** basins "away"


```{r main_mod_1, warning=FALSE, message=FALSE}
# no covariates, linear distance
# mod1_full = feols((max_cropland_EVI) ~
#                     (distance) + downstream |
#                     year +  as.factor(mine_basin),
#                   data = df_reg,
#                   cluster = "HYBAS_ID")

mod2_full = feols((max_cropland_EVI) ~
                    (distance) * downstream |
                    year +  as.factor(mine_basin),
                  data = df_reg,
                  cluster = "HYBAS_ID")

# mod3_full = feols((max_EVI) ~
#                     (distance) + downstream  |
#                     year +  as.factor(mine_basin),
#                   data = df_reg,
#                   cluster = "HYBAS_ID")

mod4_full = feols((max_EVI) ~
                    (distance) * downstream  |
                    year +  as.factor(mine_basin),
                  data = df_reg,
                  cluster = "HYBAS_ID")

# with covariates, linear distance
# mod5_full = feols((max_cropland_EVI) ~
#                     (distance) + downstream +
#                     elevation + slope + soilq_avg +
#                     tmp_max + precipitation |
#                     year + as.factor(mine_basin),
#                   data = df_reg,
#                   cluster = "HYBAS_ID")

mod6_full = feols((max_cropland_EVI) ~
                    (distance) * downstream +
                    elevation + slope + soilq_avg +
                    tmp_max + precipitation |
                    year +  as.factor(mine_basin),
                  data = df_reg,
                  cluster = "HYBAS_ID")

# mod7_full = feols((max_EVI) ~
#                     (distance) + downstream +
#                     elevation + slope + soilq_avg +
#                     tmp_max + precipitation |
#                     year +  as.factor(mine_basin),
#                   data = df_reg,
#                   cluster = "HYBAS_ID")

mod8_full = feols((max_EVI) ~
                    distance * downstream +
                    elevation + slope + soilq_avg +
                    tmp_max + precipitation |
                    year +  as.factor(mine_basin),
                  data = df_reg,
                  cluster = "HYBAS_ID")

etable(mod2_full, mod6_full, mod4_full, mod8_full)

evi_cropland_avg <- df_reg |>
  filter(!is.na(max_cropland_EVI)) |>
  pull(max_cropland_EVI) |> mean()
evi_avg <- df_reg |>
  filter(!is.na(max_EVI)) |>
  pull(max_EVI) |> mean()
```

Compared to the sample mean, the presence of a mine upstream reduces the overall EVI by **`r round(coef(mod4_full)["downstream"] / evi_avg * 100, 2)`%** (`r round(coef(mod8_full)["downstream"] / evi_avg * 100, 2)`%) and the EVI for croplands by **`r round(coef(mod2_full)["downstream"] / evi_cropland_avg * 100,2)`%** (`r round(coef(mod6_full)["downstream"] / evi_cropland_avg * 100,2)`%) on average without (with) controls.



### Sample with time/distance restrictions

This specification includes:

* all years from **2016 to 2023**
* all basin systems, regardless of area mined in the mine basin itself
* all up/downstream basins up to **5** basins "away"


```{r main_mod_2, warning=FALSE, message=FALSE}
df_reg_restr <- df_reg |> filter(order <= 5, year > 2015)

# no covariates, linear distance
# mod1_restr = feols((max_cropland_EVI) ~ (distance) + downstream |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr,
#                    cluster = "HYBAS_ID")

mod2_restr = feols((max_cropland_EVI) ~ (distance) * downstream |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr,
                   cluster = "HYBAS_ID")

# mod3_restr = feols((max_EVI) ~ (distance) + downstream |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr,
#                    cluster = "HYBAS_ID")

mod4_restr = feols((max_EVI) ~ (distance) * downstream |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr,
                   cluster = "HYBAS_ID")

# with covariates, linear distance
# mod5_restr = feols((max_cropland_EVI) ~
#                      distance + downstream +
#                      elevation + slope + soilq_avg +
#                      tmp_max + precipitation |
#                      year + as.factor(mine_basin),
#                    data = df_reg_restr,
#                    cluster = "HYBAS_ID")

mod6_restr = feols((max_cropland_EVI) ~
                     distance * downstream +
                     elevation + slope + soilq_avg +
                     tmp_max + precipitation |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr,
                   cluster = "HYBAS_ID")

# mod7_restr = feols((max_EVI) ~
#                      distance + downstream +
#                      elevation + slope + soilq_avg +
#                      tmp_max + precipitation |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr,
#                    cluster = "HYBAS_ID")

mod8_restr = feols((max_EVI) ~
                     distance * downstream +
                     elevation + slope + soilq_avg +
                     tmp_max + precipitation |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr,
                   cluster = "HYBAS_ID")

etable(mod2_restr, mod6_restr, mod4_restr, mod8_restr)

evi_cropland_avg <- df_reg_restr |>
  filter(!is.na(max_cropland_EVI)) |>
  pull(max_cropland_EVI) |> mean()
evi_avg <- df_reg_restr |>
  filter(!is.na(max_EVI)) |>
  pull(max_EVI) |> mean()
```

Compared to the sample mean, the presence of a mine upstream reduces the overall EVI by **`r round(coef(mod4_restr)["downstream"] / evi_avg * 100, 2)`%** (`r round(coef(mod8_restr)["downstream"] / evi_avg * 100, 2)`%) and the EVI for croplands by **`r round(coef(mod2_restr)["downstream"] / evi_cropland_avg * 100,2)`%** (`r round(coef(mod6_restr)["downstream"] / evi_cropland_avg * 100,2)`%) on average without (with) controls.



### Sample with mine area restrictions

This specification includes:

* all years from **2001 to 2023**
* all basin systems where mined area **>1km^2**
* all up/downstream basins up to **10** basins "away"


```{r main_mod_3, warning=FALSE, message=FALSE}
basins_large_mines <- df_reg |> filter(mine_area_km2 > 1) |> pull(mine_basin) |> unique()
df_reg_large_mines <- df_reg |> filter(mine_basin %in% basins_large_mines)

# no covariates, linear distance
# mod1_large = feols((max_cropland_EVI) ~ (distance) + downstream |
#                year +  as.factor(mine_basin),
#              data = df_reg_large_mines,
#              cluster = "HYBAS_ID")

mod2_large = feols((max_cropland_EVI) ~ (distance) * downstream |
               year +  as.factor(mine_basin),
             data = df_reg_large_mines,
             cluster = "HYBAS_ID")

# mod3_large = feols((max_EVI) ~ (distance) + downstream |
#                year +  as.factor(mine_basin),
#              data = df_reg_large_mines,
#              cluster = "HYBAS_ID")

mod4_large = feols((max_EVI) ~ (distance) * downstream |
               year +  as.factor(mine_basin),
             data = df_reg_large_mines,
             cluster = "HYBAS_ID")

# with covariates, linear distance
# mod5_large = feols((max_cropland_EVI) ~
#                distance + downstream +
#                elevation + slope + soilq_avg +
#                tmp_max + precipitation |
#                year + as.factor(mine_basin),
#              data = df_reg_large_mines,
#              cluster = "HYBAS_ID")

mod6_large = feols((max_cropland_EVI) ~
               distance * downstream +
               elevation + slope + soilq_avg +
               tmp_max + precipitation |
               year +  as.factor(mine_basin),
             data = df_reg_large_mines,
             cluster = "HYBAS_ID")

# mod7_large = feols((max_EVI) ~
#                distance + downstream +
#                elevation + slope + soilq_avg +
#                tmp_max + precipitation |
#                year +  as.factor(mine_basin),
#              data = df_reg_large_mines,
#              cluster = "HYBAS_ID")

mod8_large = feols((max_EVI) ~
               distance * downstream +
               elevation + slope + soilq_avg +
               tmp_max + precipitation |
               year +  as.factor(mine_basin),
             data = df_reg_large_mines,
             cluster = "HYBAS_ID")

etable(mod2_large, mod6_large, mod4_large, mod8_large)

evi_cropland_avg <- df_reg_large_mines |>
  filter(!is.na(max_cropland_EVI)) |>
  pull(max_cropland_EVI) |> mean()
evi_avg <- df_reg_large_mines |>
  filter(!is.na(max_EVI)) |>
  pull(max_EVI) |> mean()
```

Compared to the sample mean, the presence of a mine upstream reduces the overall EVI by **`r round(coef(mod4_large)["downstream"] / evi_avg * 100, 2)`%** (`r round(coef(mod8_large)["downstream"] / evi_avg * 100, 2)`%) and the EVI for croplands by **`r round(coef(mod2_large)["downstream"] / evi_cropland_avg * 100,2)`%** (`r round(coef(mod6_large)["downstream"] / evi_cropland_avg * 100,2)`%) on average without (with) controls.


### Sample with time/distance and mine area restrictions

This specification includes:

* all years from **2016 to 2023**
* all basin systems where mined area **>1km^2**
* all up/downstream basins up to **5** basins "away"


```{r main_mod_4, warning=FALSE, message=FALSE}
df_reg_restr_large <- df_reg_large_mines |> filter(order <= 5, year > 2015)

# no covariates, linear distance
# mod1_restr_large = feols((max_cropland_EVI) ~ (distance) + downstream |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr_large,
#                    cluster = "HYBAS_ID")

mod2_restr_large = feols((max_cropland_EVI) ~ (distance) * downstream |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr_large,
                   cluster = "HYBAS_ID")

# mod3_restr_large = feols((max_EVI) ~ (distance) + downstream |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr_large,
#                    cluster = "HYBAS_ID")

mod4_restr_large = feols((max_EVI) ~ (distance) * downstream |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr_large,
                   cluster = "HYBAS_ID")

# with covariates, linear distance
# mod5_restr_large = feols((max_cropland_EVI) ~
#                      distance + downstream +
#                      elevation + slope + soilq_avg +
#                      tmp_max + precipitation |
#                      year + as.factor(mine_basin),
#                    data = df_reg_restr_large,
#                    cluster = "HYBAS_ID")

mod6_restr_large = feols((max_cropland_EVI) ~
                     distance * downstream +
                     elevation + slope + soilq_avg +
                     tmp_max + precipitation |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr_large,
                   cluster = "HYBAS_ID")

# mod7_restr_large = feols((max_EVI) ~
#                      distance + downstream +
#                      elevation + slope + soilq_avg +
#                      tmp_max + precipitation |
#                      year +  as.factor(mine_basin),
#                    data = df_reg_restr_large,
#                    cluster = "HYBAS_ID")

mod8_restr_large = feols((max_EVI) ~
                     distance * downstream +
                     elevation + slope + soilq_avg +
                     tmp_max + precipitation |
                     year +  as.factor(mine_basin),
                   data = df_reg_restr_large,
                   cluster = "HYBAS_ID")

etable(mod2_restr_large, mod6_restr_large, mod4_restr_large, mod8_restr_large)

evi_cropland_avg <- df_reg_restr_large |>
  filter(!is.na(max_cropland_EVI)) |>
  pull(max_cropland_EVI) |> mean()
evi_avg <- df_reg_restr_large |>
  filter(!is.na(max_EVI)) |>
  pull(max_EVI) |> mean()
```

Compared to the sample mean, the presence of a mine upstream reduces the overall EVI by **`r round(coef(mod4_restr_large)["downstream"] / evi_avg * 100, 2)`%** (`r round(coef(mod8_restr_large)["downstream"] / evi_avg * 100, 2)`%) and the EVI for croplands by **`r round(coef(mod2_restr_large)["downstream"] / evi_cropland_avg * 100,2)`%** (`r round(coef(mod6_restr_large)["downstream"] / evi_cropland_avg * 100,2)`%) on average without (with) controls.



## Robustness


## Heterogeneity



